Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-29 ms.tex
Modifying description of rs

In the opposite limit of weak heating ($v_{w} \ll \sigma_0$), the
stagnation radius moves towards the break radius, $\rb$ in the stellar
density profile, formally implying that almost entire ISM of the
galaxy is accreting.  This result makes intuitive sense: gas is
supplied to the nuclear by stars which are gravitationally bound to
the black hole, so outflows are possible only if the specific heating
rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational
binding energy.
%   In fact, for core galaxies the specific
% heating rate necessary to produce an unbound outflow can greatly
% exceed $\sigma^{2}$ due to the additional gravitational potential of
% stars outside the sphere of influence (Appendix~\ref{app:be}).

>>>>

In the opposite limit of weak heating ($v_w\lsim \sigma_0$) the
stagnation radius moves towards the break radius, $\rb$ in the stellar
density profile, formally implying that almost entire ISM of the
galaxy is accreting.  This result makes intuitive sense: gas is
supplied to the nuclear by stars which are gravitationally bound to
the black hole, so outflows are possible only if the specific heating
rate $\sim v_{w}^{2}$ significantly exceeds the specific gravitational
binding energy.

More precisely we find that there is a critical $\zeta_c$
($\zeta\equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$), such that if
$\zeta\lsim\zeta_c$, then $\rs\simeq\rb$. For $\rb\gsim\rsoi$ we find

\begin{align}
\zeta_c\simeq \left(\frac{\rb}{\rsoi}\right)^{0.5(1-\Gamma)},
\end{align}

as described in Appendix~\ref{app:be}.
